Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
regression figures are now better

Imagine that you are asked to write a program to edit some text, and
told that you should change the text ``Nancy FreeHafer'' to
``Dr. Nancy''.  From this example, you likely infer that ``Jane
Goodall'' goes to ``Dr. Jane'', drawing upon your prior knowledge of
text, like that words are separated by spaces. For few-shot program learning problems
like these, the program synthesis and AI communities have had many successes,
not just for text editing~\cite{gulwani2011automating} but also for graphics
programs~\cite{ellis2017learning}, planning
procedures~\cite{devlin2017neural}, and many others.  However, the
success of these systems hinges upon having a carefully
hand-engineered \textbf{Domain Specific Language (DSL)}.  DSLs
impart prior knowledge of a domain
by providing a restricted set
of finely-tuned programming primitives: for
%that are finely tuned to the problems in the domain: for
text editing,
these are primitives like appending and splitting on characters.
In this work,
we consider the problem of
building agents that solve program learning tasks,
and also the problem of acquiring
the prior knowledge necessary to quickly
solve these tasks (Figure~\ref{firstPageFigure}).
Our solution is an algorithm that learns a DSL
while jointly training a neural network to help write programs in the learned DSL.
\begin{figure}[h]
  \begin{minipage}[c]{0.68\textwidth}
\hspace{-0.5cm}      \begin{tabular}{r|c|}\cmidrule{2-2}
  \sc{Task}&
  \begin{tabular}{rcl}
  Nancy FreeHafer&$\longrightarrow$& Dr. Nancy\\
% Andrew Cencici&$\longrightarrow$&Dr. Andrew\\
 Jane Goodall&$\longrightarrow$&???
  \end{tabular}\\\cmidrule{2-2}
  \sc{Program}&$f(\text{\code{s}})\,=\,$\code{(}$f_0$\code{ "Dr." (}$f_1$\code{ s ' '))}\\\cmidrule{2-2}
    \sc{DSL}
&\begin{tabular}{l}
    $f_0($\code{a}$,$\code{b}$) \,=\, $\code{(fold a b ($\lambda$ (x y)}\\
    \phantom{$f_0($\code{a}$,$\code{b}$) \,=\, $\code{(}}\code{(cons x y)))}\\
    \hspace{0.5cm}($f_0$: \emph{Appends lists (of characters))}\\
    $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(fold s s ($\lambda$ (x a)}\\
    \phantom{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{  }}\code{(if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
    \end{tabular}\\\cmidrule{2-2}
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[c]{0.31\textwidth}
      \caption{\textbf{Task}: Few-shot learning problem. Model solves tasks by writing \textbf{program}s, and jointly learns a library of reusable subroutines that are shared across multiple tasks, called a \textbf{Domain Specific Language (DSL)}. Program writing is guided by a neural network trained jointly with the library.}\label{firstPageFigure}
    \end{minipage}
\end{figure}

@@

        \STATE $\mathcal{D},\theta\gets $induceDSL$(\{\mathcal{F}^{\theta}_x\cup\mathcal{F}^{q}_x\}_{x\in X})$  \hspace{1.1cm} \footnotesize{\textbf{(Compress)}}
        %% \STATE Define $Q_x(z) \propto \begin{cases}
        %%   \probability[x|z]\probability[z|\mathcal{D}_i,\theta_i]&x\in \mathcal{F}_x\\
        %%   0&x\not \in \mathcal{F}_x
        %% \end{cases}
        \ENDFOR
        \STATE \textbf{return} $\mathcal{D},\theta,q$
      \end{algorithmic}
    \end{algorithm}
  \end{minipage}
\vspace{-0.7cm}\end{wrapfigure}%% To appropriately score each proposed $\mathcal{D}$ we must reestimate the weight vector $\theta$.
%% Although this  may seem 
%% very similar to estimating the parameters of a probabilistic context free grammar,
%% for which we have effective approaches like the Inside/Outside algorithm~\cite{international2000derivation},
%% our DSLs are context-sensitive due to the presence of variables
%% in the programs and also due to the polymorphic typing system.
%% In the Supplement we derive a tractable MAP estimator for $\theta$.
Putting all these ingredients together, Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
\begin{figure*}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{(lambda (a b) (foldr b (cons "," a)}\\
      \phantom{\code{(lambda }}\code{(lambda (x z) (cons x z))))}\\
      \code{(lambda (a b) (foldr a b }\\
      \phantom{\code{(lambda }}\code{(lambda (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b (lambda (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{(lambda (s) (map (lambda (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{(lambda (s) (map (lambda (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{(lambda (s) (map (lambda (x)}\\\hspace{0.2cm}\code{   (if (= x '-') ',' x))) s)}
      \end{tabular}
\\\bottomrule
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{figure*}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{l}
    \toprule
    $f_0($\code{i$,\ell$}$) \,=\, $\code{(singleton (index i $\ell$))}\\
    \hspace{0.5cm}($f_0$: \emph{Put the $i$-th index into a list})\\
    $f_1($\code{i$,\ell$}$) \,=\, $\code{(++ $\ell$ ($f_0$ i $\ell$))}\\
    \hspace{0.5cm}($f_1$: \emph{Append the $i$-th index})\\
    $f_2($\code{n$,\ell$}$) \,=\, $\code{(any (lambda (x) (= n x)) $\ell$)}\\
    \hspace{0.5cm}($f_1$: \emph{Whether $n$ appears in the list})\\
    $f_3($\code{i$,\ell$}$) \,=\, $\code{(index (negate i) (sort $\ell$))}\\
    \hspace{0.5cm}($f_3$: \emph{Get the $i$-th largest number})\\
    $f_4($\code{n$,\ell$}$) \,=\, $\code{(mapi (lambda (i x) (mod x n)) $\ell$)}\\
    $f_5($\code{k$,\ell$}$) \,=\, $\code{(mapi (lambda (i x) (+ x k)) $\ell$)}\\
    $f_6($\code{k$,$n$,\ell$}$) \,=\, $\code{($f_4$ n ($f_5$ k $\ell$)}\\
    \hspace{0.5cm}($f_6$: \emph{Caesar shift of $k$ in integers modulo $n$})\\
  \bottomrule
  \end{tabular}
  \caption{Some learned DSL primitives for list functions}\label{listinduced}
\end{table}

@@

How well does the  learned DSL generalized to real text-editing scenarios?
We tested, but did not train, our system on problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems with an average search time of 235 seconds.
After learning,
it solves 74.1\%, and does so much faster,
solving them in an average of 29 seconds.
As of the 2017 SyGuS competition,
the best-performing algorithm solves 79.6\% problems.
But, SyGuS comes with a
different hand-engineered DSL \emph{for each text editing problem}.
Here  we learned a single DSL
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

\begin{table}[t]
  \centering
    \begin{tabular}{l}
      \toprule
      $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map (lambda (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s (lambda (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty? car (lambda (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words. See Fig.~\ref{initialExampleDSL}})\\
        $f_3($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s (lambda (x a) (if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_3$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
        %(lambda (lambda (fold $0 $0 (lambda (lambda (if (char-eq? $1 $3) empty (cons $1 $0)))))))
  \\\bottomrule
    \end{tabular}
  \caption{Some string editing learned subroutines }\label{textPrimitives}
  \end{table}

\begin{wrapfigure}{r}{0.6\textwidth}
  \centering\begin{tabular}{c}\toprule
+106 769-858-438 $\longrightarrow$106.769.858.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
+83 973-757-831 $\longrightarrow$83.973.757.831%& Andrew Cencici $\longrightarrow$ Dr. Andrew
%DkI$>$DwKI$<$xaPoc& 	DWKI\\
%KfvTh$>$Dbl$<$OIJso 	&DBL
\\\midrule
%(lambda (#(lambda (lambda (map (lambda (if (char-eq? $0 $1) $2 $0))))) '.' SPACE (#(lambda (lambda (map (lambda (if (char-eq? $0 $1) $2 $0))))) '.' '-' (cdr $0))))
\multicolumn{1}{c}{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  '.' ' ' ($f_0$ '.' '-' (cdr s)))}}
%\multicolumn{1}{l}{$f(\text{\code{s}}) = $\code{(}$f_0$\code{ "Dr. " (}$f_3$\code{ s " "))}}
\\
\bottomrule
  \end{tabular}

  %% \vspace{0.25cm}

  %% \begin{minipage}{\linewidth}
  %%   \centering
  %%   $f($\code{s}$) \,=\, $
  %% \end{minipage}

  \caption{String edit task (top) and the program \system writes for it (bottom). $f_0$ is a subroutine written by \systemEnding, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.3\textwidth} \newcommand{\functionSize}{0.75cm}\vspace{-0.5cm}
  \includegraphics[width = \functionSize]{figures/functions/0.png}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/207.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/317.png}\\  
  \includegraphics[width = \functionSize]{figures/functions/432.png}
  \includegraphics[width = \functionSize]{figures/functions/415.png}
  \includegraphics[width = \functionSize]{figures/functions/426.png}
  \includegraphics[width = \functionSize]{figures/functions/597.png}
  \includegraphics[width = \functionSize]{figures/functions/591.png}
  \caption{Recognition model input for symbolic regression. While the DSL learns subroutines for rational functions \& polynomials, the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines is appropriate for explaining the observation.}\label{functions}
\end{wrapfigure}
%% \begin{align*}
%%   \log \probability[x|p] \triangleq& \sum_{n\leq N}\log
%%   \mathcal{N}(p(i_n,\vec{\mathcal{R}}^*)|o_n) - \frac{D\log N}{2}
%% \end{align*}

@@

  \\\midrule\multicolumn{6}{c}{\emph{Symbolic Regression}}\\\midrule
  \% solved&   \textbf{84\% }&75\%&38\%&38\%&37\% \\
  Solve time&  24s& 40s  &31s&55s&29s\\
  %% MDL (nats)&   9.3 &11.0&2.3&--&4.6

>>>>

Imagine you are asked  to edit some text, and
told that you should change the text ``Nancy FreeHafer'' to
``Dr. Nancy''.  From this example, you likely infer that ``Jane
Goodall'' goes to ``Dr. Jane'', drawing upon your prior knowledge of
text, like that words are separated by spaces. Few-shot learning problems
like these
are commonplace in both human and machine learning,

, the program synthesis and AI communities have had many successes,
not just for text editing~\cite{gulwani2011automating} but also for graphics
programs~\cite{ellis2017learning}, planning
procedures~\cite{devlin2017neural}, and many others.  However, the
success of these systems hinges upon having a carefully
hand-engineered \textbf{Domain Specific Language (DSL)}.  DSLs
impart prior knowledge of a domain
by providing a restricted set
of finely-tuned programming primitives: for
%that are finely tuned to the problems in the domain: for
text editing,
these are primitives like appending and splitting on characters.
In this work,
we consider the problem of
building agents that solve program learning tasks,
and also the problem of acquiring
the prior knowledge necessary to quickly
solve these tasks (Figure~\ref{firstPageFigure}).
Our solution is an algorithm that learns a DSL
while jointly training a neural network to help write programs in the learned DSL.
\begin{figure}[h]
  \begin{minipage}[c]{0.68\textwidth}
\hspace{-0.5cm}      \begin{tabular}{r|c|}\cmidrule{2-2}
  \sc{Task}&
  \begin{tabular}{rcl}
  Nancy FreeHafer&$\longrightarrow$& Dr. Nancy\\
% Andrew Cencici&$\longrightarrow$&Dr. Andrew\\
 Jane Goodall&$\longrightarrow$&???
  \end{tabular}\\\cmidrule{2-2}
  \sc{Program}&$f(\text{\code{s}})\,=\,$\code{(}$f_0$\code{ "Dr." (}$f_1$\code{ s ' '))}\\\cmidrule{2-2}
    \sc{DSL}
&\begin{tabular}{l}
    $f_0($\code{a}$,$\code{b}$) \,=\, $\code{(fold a b ($\lambda$ (x y)}\\
    \phantom{$f_0($\code{a}$,$\code{b}$) \,=\, $\code{(}}\code{(cons x y)))}\\
    \hspace{0.5cm}($f_0$: \emph{Appends lists (of characters))}\\
    $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(fold s s ($\lambda$ (x a)}\\
    \phantom{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{  }}\code{(if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
    \end{tabular}\\\cmidrule{2-2}
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[c]{0.31\textwidth}
      \caption{\textbf{Task}: Few-shot learning problem. Model solves tasks by writing \textbf{program}s, and jointly learns a library of reusable subroutines that are shared across multiple tasks, called a \textbf{Domain Specific Language (DSL)}. Program writing is guided by a neural network trained jointly with the library.}\label{firstPageFigure}
    \end{minipage}
\end{figure}

@@

        \STATE $\mathcal{D},\theta\gets $induceDSL$(\{\mathcal{F}^{\theta}_x\cup\mathcal{F}^{q}_x\}_{x\in X})$  \hspace{1.1cm} \footnotesize{\textbf{(Compress)}}
        %% \STATE Define $Q_x(z) \propto \begin{cases}
        %%   \probability[x|z]\probability[z|\mathcal{D}_i,\theta_i]&x\in \mathcal{F}_x\\
        %%   0&x\not \in \mathcal{F}_x
        %% \end{cases}
        \ENDFOR
        \STATE \textbf{return} $\mathcal{D},\theta,q$
      \end{algorithmic}
    \end{algorithm}
  \end{minipage}
\vspace{-0.7cm}\end{wrapfigure}%% To appropriately score each proposed $\mathcal{D}$ we must reestimate the weight vector $\theta$.
%% Although this  may seem 
%% very similar to estimating the parameters of a probabilistic context free grammar,
%% for which we have effective approaches like the Inside/Outside algorithm~\cite{international2000derivation},
%% our DSLs are context-sensitive due to the presence of variables
%% in the programs and also due to the polymorphic typing system.
%% In the Supplement we derive a tractable MAP estimator for $\theta$.
Putting all these ingredients together, Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
\begin{figure*}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (a b) (foldr b (cons "," a)}\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}\\
      \code{($\lambda$ (a b) (foldr a b }\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b ($\lambda$ (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x '-') ',' x))) s)}
      \end{tabular}
\\\bottomrule
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{figure*}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{l}
    \toprule
    $f_0($\code{i$,\ell$}$) \,=\, $\code{(singleton (index i $\ell$))}\\
    \hspace{0.5cm}($f_0$: \emph{Put the $i$-th index into a list})\\
    $f_1($\code{i$,\ell$}$) \,=\, $\code{(++ $\ell$ ($f_0$ i $\ell$))}\\
    \hspace{0.5cm}($f_1$: \emph{Append the $i$-th index})\\
    $f_2($\code{n$,\ell$}$) \,=\, $\code{(any ($\lambda$ (x) (= n x)) $\ell$)}\\
    \hspace{0.5cm}($f_1$: \emph{Whether $n$ appears in the list})\\
    $f_3($\code{i$,\ell$}$) \,=\, $\code{(index (negate i) (sort $\ell$))}\\
    \hspace{0.5cm}($f_3$: \emph{Get the $i$-th largest number})\\
    $f_4($\code{n$,\ell$}$) \,=\, $\code{(mapi ($\lambda$ (i x) (mod x n)) $\ell$)}\\
    $f_5($\code{k$,\ell$}$) \,=\, $\code{(mapi ($\lambda$ (i x) (+ x k)) $\ell$)}\\
    $f_6($\code{k$,$n$,\ell$}$) \,=\, $\code{($f_4$ n ($f_5$ k $\ell$)}\\
    \hspace{0.5cm}($f_6$: \emph{Caesar shift of $k$ in integers modulo $n$})\\
  \bottomrule
  \end{tabular}
  \caption{Some learned DSL primitives for list functions}\label{listinduced}
\end{table}

@@

How well does the  learned DSL generalized to real text-editing scenarios?
We tested, but did not train, our system on problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems with an average search time of 235 seconds.
After learning,
it solves 74.1\%, and does so much faster,
solving them in an average of 29 seconds.
As of the 2017 SyGuS competition,
the best-performing algorithm solves 79.6\% of the problems.
But, SyGuS comes with a
different hand-engineered DSL \emph{for each text editing problem}.
Here  we learned a single DSL
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

\begin{table}[t]
  \centering
    \begin{tabular}{l}
      \toprule
      $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty? car ($\lambda$ (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words. See Fig.~\ref{initialExampleDSL}})\\
        $f_3($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_3$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
        %($\lambda$ ($\lambda$ (fold $0 $0 ($\lambda$ ($\lambda$ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
  \\\bottomrule
    \end{tabular}
  \caption{Some string editing learned subroutines }\label{textPrimitives}
  \end{table}

%% \begin{wrapfigure}{r}{0.6\textwidth}
%%   \centering\begin{tabular}{c}\toprule
%% +106 769-858-438 $\longrightarrow$106.769.858.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
%% +83 973-757-831 $\longrightarrow$83.973.757.831%& Andrew Cencici $\longrightarrow$ Dr. Andrew
%% %DkI$>$DwKI$<$xaPoc& 	DWKI\\
%% %KfvTh$>$Dbl$<$OIJso 	&DBL
%% \\\midrule
%% %(lambda (#(lambda (lambda (map (lambda (if (char-eq? $0 $1) $2 $0))))) '.' SPACE (#(lambda (lambda (map (lambda (if (char-eq? $0 $1) $2 $0))))) '.' '-' (cdr $0))))
%% \multicolumn{1}{c}{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  '.' ' ' ($f_0$ '.' '-' (cdr s)))}}
%% %\multicolumn{1}{l}{$f(\text{\code{s}}) = $\code{(}$f_0$\code{ "Dr. " (}$f_3$\code{ s " "))}}
%% \\
%% \bottomrule
%%   \end{tabular}

%%   %% \vspace{0.25cm}

%%   %% \begin{minipage}{\linewidth}
%%   %%   \centering
%%   %%   $f($\code{s}$) \,=\, $
%%   %% \end{minipage}

%%   \caption{String edit task (top) and the program \system writes for it (bottom). $f_0$ is a subroutine written by \systemEnding, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
%% \end{wrapfigure}

@@

\begin{wrapfigure}{r}{6.4cm} \newcommand{\functionSize}{1.5cm}\vspace{-0.5cm}\centering
%  \includegraphics[width = \functionSize]{figures/functions/0.png}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/116.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/149.png}
  %% \includegraphics[width = \functionSize]{figures/functions/432.png}
  %% \includegraphics[width = \functionSize]{figures/functions/415.png}
  %% \includegraphics[width = \functionSize]{figures/functions/426.png}
  %% \includegraphics[width = \functionSize]{figures/functions/597.png}
  %% \includegraphics[width = \functionSize]{figures/functions/591.png}
  \caption{Recognition model input for symbolic regression. While the DSL learns subroutines for rational functions \& polynomials, the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines is appropriate for explaining the observation.}\label{functions}
\end{wrapfigure}
%% \begin{align*}
%%   \log \probability[x|p] \triangleq& \sum_{n\leq N}\log
%%   \mathcal{N}(p(i_n,\vec{\mathcal{R}}^*)|o_n) - \frac{D\log N}{2}
%% \end{align*}

@@

  \\\midrule\multicolumn{6}{c}{\emph{Symbolic Regression}}\\\midrule
  \% solved&   \textbf{84\% }&75\%&38\%&38\%&37\% \\
  Solve time&  24s& 40s  &31s&55s&29s
  %% MDL (nats)&   9.3 &11.0&2.3&--&4.6
